Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Low-Complexity CSI Feedback for FDD Massive MIMO Systems via Learning to Optimize

@@

>>>>

Ma \textit{et al.} \cite{Ma2024} present a novel learning-to-optimize (L2O) framework that combines compressive sensing with deep learning for efficient CSI feedback. Their Csi-L2O approach achieves state-of-the-art performance (-18.88 dB NMSE) while reducing encoder complexity to just 0.15\% of conventional methods through innovative linear projection and LSTM-based optimization.

@@

	\bibitem{Ma2024} 
	Y. Ma, H. He, S. Song, J. Zhang, and K. B. Letaief, 
	``Low-Complexity CSI Feedback for FDD Massive MIMO Systems via Learning to Optimize,'' 
	\textit{arXiv preprint arXiv:2406.16323}, 2024.
